A Switching Planner for Combined Task and Observation Planning

### 2011-02-09 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/switching.tex
typo

Given \switchAction, we also include another once-only self-transition
action $\actions.\poss(\switchAction)$, the \emph{confirmation action}
with the reward property:

>>>>

Given \switchAction, we also include another once-only self-transition
action $\actions.\poss(\switchAction)$, a \emph{confirmation action}
with the reward property:
